Cycle Route Uptake and Scenario Estimation (CRUSE): an approach for developing strategic cycle network planning tools

### 2024-08-06 paper.qmd
Add acknowledgements

\[To be added post review.\]

>>>>

Thanks to Catherine Swift and Ciaran Maguire for their support in the development of the CRUSE Tool during the early stages.
Thanks to everyone who attended the workshops and provided feedback on the tool, especially Dónal Hodgins, Kieran Cullinane, and Declan Keenan.
Thanks to Yael Arbell for comments on an earlier version of the manuscript that informed discussion of stakeholder engagement.
Finally, thanks and to the European Transport Research Review staff and to the anonymous reviewers for their constructive feedback.
